Hybrid Threads for the Parrot Virtual Machine

### 2012-02-25 Paper.tex
A few words on proxies

\section{PMCs}

@@

Proxies are the arbiters between threads. They are the only means for a thread to access another thread's data and are implemented by the \textit{Proxy} PMC type.

>>>>

\section{PMCs}
\label{sec:PMCs}

@@

Proxies are the arbiters between threads. They are the only means for a thread to access another thread's data and are implemented by the \textit{Proxy} PMC type. This type has only to attributes, none of which are garbage collected:
%
\begin{itemize}
\item PMC *target: The PMC this object proxies to
\item Parrot\_Interp interp: The interpreter owning target
\end{itemize}

As described in section~\ref{sec:PMCs} PMC source files to get preprocessed before compilation by a C compiler. This preprocessing gets done by the \textit{tools/build/pmc2c.pl} Perl script. This script got extended by implementing the \textit{Parrot::Pmc2c::PMC::Proxy} module which creates default implementations for all vtable functions not otherwise defined in the \textit{proxy.pmc} file. The default implementation for all writing functions would just call \textit{cant\_do\_write\_method} which creates a runtime exception. All other methods call the vtable method of the same name on the \textit{target} passing \textit{interp} as the current interpreter and all other parameters unchanged. If the method returns a PMC, another proxy object is created and wrapped around it so it may be safely returned to the caller.
